Edge sign prediction in general graphs and Correlation Clustering

### 2017-08-24 cc/cc_multimincut_stable.tex
reorganize files and write some intro
move text around for a state of the art following more the general direction of chapter

We first give more details on the equivalence between \mmc{} and \pcc{},
following~\autocite{Demaine2006} but omitting the full proofs to avoid redundancy. Recall that given
a weighted graph $H=(V_H, E_H, w_H)$ and a collection of $k$ sources and targets
$S=\{(s_i,t_i)\}_{i=1}^k \in V_H^2$, in \mmc{} we want to find the lightest set of edges $T\in E_H$
whose removal disconnects every pair $s_i$ from the corresponding $t_i$. Let us first describe a
polynomial reduction from \mmc{} to \pcc{}. Namely, given an instance $(H, S)$ of \mmc{}, we let
$W_H=\sum_{e\in E_H} w_H(e)$ be the total weight of $H$ and $G_H$ be the same graph as $H$ with all
its edges labeled positively. We then connect every pair $(s_i, t_i)$ by a negative edge of weight
$W_H+1$. One can check (\autocite[Theorem 4.7]{Demaine2006}) that a multicut $T$ in $H$ with weight
$W$ induces a clustering in $G_H$ of weighted disagreement $W$ by the connected components of
$G^+\setminus T$. Likewise, a clustering of $G_H$ with weight $W$ induces a multicut on $H$ with
weight as most $W$. In the unweighted case, the reduction is similar but the heavy negative edges
are simulated in the following way: include every source and target in a clique of $n$ nodes and
connect that clique to the corresponding source or target by $n$ negative edges.

We next present the polynomial reduction from \pcc{} to \mmc{}. Given $G=(V, (E^+, E^-), w)$ we let
$H_G$ be the graph induced by $E^+$ with the same weight. Then for every negative edge $(u,v)$ of
weight $w_{uv}^-$, we create a new vertex $v_{\widehat{uv}}$, connect $u$ to $v_{\widehat{uv}}$ with
weight $w_{uv}^-$ and let $(v_{\widehat{uv}}, v)$ be a source-target pair added to $S_G$. This
construction is depicted in \autoref{fig:cc_mmc} and one can show (\autocite[Theorem
4.4]{Demaine2006})\Todo{give the intuition of the proof} that it takes a linear time to construct a
multicut of weight $W$ in $H_G$ from a clustering of weight $W$ in $G$, and vice versa.

\begin{figure}[htpb]
   \centering
   \includegraphics[width=0.8\linewidth]{assets/raw/cc_to_mmc.png}
   \caption{The transformation from \pcc{} on $G$ to \mmc{} on $H$ (temporarily reproduced from
   \autocite{Demaine2006}) \label{fig:cc_mmc}}
\end{figure}

@@

\Textcite{StableCC17} provide a robust algorithm for $2-\nicefrac{2}{k}$-stable instance of
$k$-\textsc{Minimum Multiway Cut}, which therefore is not really useful in our case because I confused
multiway cut and multicut. To be fair, it seems I'm not the only one, \href{http://pages.cs.wisc.edu/~shuchi/papers/multicut-hardness-full.pdf}{on the hardness of
   approximating multicut}
   \enquote{multicut is known to be APX-hard
      (\href{https://pdfs.semanticscholar.org/1cf6/4c2bdd4f1c384a55910606a64c8d831a96ba.pdf}%
   {Dahlhaus et al. 1994}).} by that 1994 paper define the multiway cut problem, see
   \autoref{fig:cc_multiwhat}. \Textcite[Theorem 24]{Bansal2004} show that we can go from
   \textsc{Minimum Multiway Cut} to \pcc{} but I doubt about the other direction, mostly because
   \textsc{Minimum Multiway Cut} can actually be approximated with factor smaller than $1.3$.
   see \url{http://www.nowozin.net/sebastian/papers/nowozin2009lpstability.pdf} about LP multicut
   stability.
\begin{figure}[htpb]
   \centering
   \includegraphics[width=0.9\linewidth]{assets/raw/multicut_vs_multiway.png}
   \caption{Confusing statement} \label{fig:cc_multiwhat}
\end{figure}

>>>>

@@

\iffalse
\Textcite{StableCC17} provide a robust algorithm for $2-\nicefrac{2}{k}$-stable instance of
$k$-\textsc{Minimum Multiway Cut}, which therefore is not really useful in our case because I confused
multiway cut and multicut. To be fair, it seems I'm not the only one, \href{http://pages.cs.wisc.edu/~shuchi/papers/multicut-hardness-full.pdf}{on the hardness of
   approximating multicut}
   \enquote{multicut is known to be APX-hard
      (\href{https://pdfs.semanticscholar.org/1cf6/4c2bdd4f1c384a55910606a64c8d831a96ba.pdf}%
   {Dahlhaus et al. 1994}).} by that 1994 paper define the multiway cut problem, see
   \autoref{fig:cc_multiwhat}. \Textcite[Theorem 24]{Bansal2004} show that we can go from
   \textsc{Minimum Multiway Cut} to \pcc{} but I doubt about the other direction, mostly because
   \textsc{Minimum Multiway Cut} can actually be approximated with factor smaller than $1.3$.
   see \url{http://www.nowozin.net/sebastian/papers/nowozin2009lpstability.pdf} about LP multicut
   stability.
\begin{figure}[htpb]
   \centering
   \includegraphics[width=0.9\linewidth]{assets/raw/multicut_vs_multiway.png}
   \caption{Confusing statement} \label{fig:cc_multiwhat}
\end{figure}
\fi

### 2017-08-24 cc/cc_state_of_art.tex
move text around for a state of the art following more the general direction of chapter

We already described methods based on LP and SDP, as they have proved to be the best way to obtain
tight approximations in the worst case. Here we survey other kind of approaches with different aims.

\paragraph{Exact methods} Because of the complexity of the \pcc{} we presented earlier, one has to
rely on approximations to solve large instances of the problem. However, we can imagine offline
signed social networks with only few nodes, in which case it is reasonable to expect finding the
optimal clustering. Furthermore, this can also be useful to evaluate in practice the quality of
heuristic methods, albeit in non asymptotic setting. The most straightforward idea is to use the
formulation of the LP \eqref{eq:mindLP} with the additional constraints that all variable are
binary. \Textcite{ExactMIP13} solve this binary integer program on random instances and show that
depending on the negative edge density, the FICO Xpress solver starts to be unable to finish within
a one-hour time limit when $n \geq 40$.
\Textcite{Aref2016} describe four linear and quadratic  binary integer problems
to model \pcc{} with two clusters along with some preprocessing optimizations. With the Gurobi
software, they solve instances with up to $3200$ edges in less than a second. They also sketch
extensions to weighted graphs and more than two clusters.
In a different direction, \textcite{Berg2015}, encode the linear and quadratic integer formulations
into weighted MaxSAT instances and use the state of the art solver
MaxHS\footnote{\href{http://www.maxhs.org/}{http://maxhs.org}}~\autocite{SATSolver13} to get the
exact solution on instances with at most $1000$ nodes in less than a few hours.

\paragraph{\textsc{Cluster editing}}
\label{par:cc_editing}

@@

@@

\paragraph{Heuristic methods}

@@

% something about local minima when defining another energy function, and how it is achieved by a
% dynamic model but to be honest it has little to do with clustering {Marvel2009landscape}
% Kappes2016 \enquote{Furthermore, due to the lack of an external field (unary terms), any permutation of an
% optimal assignment results in another optimal labeling.}
% like an ICML'17 paper that touches something very related (multicut) and gives recent applications in
% vision https://arxiv.org/abs/1503.03791 represents a cut by the set of interclusters edges

>>>>

As we saw, solving \pcc{} on a training set would give us a principled way of predicting edge signs.
In this section, we thus look at existing methods for \pcc{}. We start with exact methods and fixed
parameter algorithms on complete graphs, noting they implicitly assume our learning bias. However,
in practice, these methods do not scale well, especially if their assumptions are not met. Indeed,
we next present hardness results about \pcc{}, namely that it is \NPh{} to approximate with some
constant factor greater than one, and then describe some proposed approximations. Whereas this
sounds like bad news for us, we show that heuristics can solve large instances with satisfactory
results. We conclude by further highlighting the learning aspect of \pcc{}, describing approaches in
the active and online settings.

\subsubsection{Exact methods}
\label{ssub:cc_exact_methods}

\paragraph{Complete graphs}
\label{par:cc_editing}

@@

See \url{http://fpt.wikidot.com/fpt-races} and
\url{http://fpt.wikidot.com/complexity-status-of-edge-modification-problems} for parameterized
papers on \mmc{} and \textsc{Cluster Editing}.

\paragraph{General graphs}

Because of the complexity of the \pcc{} we presented earlier, one has to
rely on approximations to solve large instances of the problem. However, we can imagine offline
signed social networks with only few nodes, in which case it is reasonable to expect finding the
optimal clustering. Furthermore, this can also be useful to evaluate in practice the quality of
heuristic methods, albeit in non asymptotic setting. The most straightforward idea is to use the
formulation of the LP \eqref{eq:mindLP} with the additional constraints that all variable are
binary.

Assign a binary variable $x_{uv}$ to each pair
of nodes (so that $x_{uv}=x_{vu}$). For a given clustering \cluster{}, let $x_{uv} = 0$ if $u$ and
$v$ are in the same cluster and $x_{uv}=1$ is $u$ and $v$ are in different clusters. Noting that
$1-x_{uv}$ is $1$ if the edge $(u,v)$ is within a cluster and $0$ otherwise, the weighted
number of disagreements is then $w(\cluster{}) = \sum_{(u,v)\in E^-} w_{uv}(1-x_{uv}) +
\sum_{(u,v)\in E^+} w_{uv}x_{uv}$. By construction, if edges $(u,v)$ and $(v,w)$ are within the same
cluster, then $(v, w)$ is also within that cluster. In terms of $x$ variable, we have that $x_{uv}=0
\wedge x_{vw}=0 \implies x_{uw} = 0$. For $x$ to be a valid cluster assignment, we thus require that all
variables are either $0$ or $1$ and respect the triangle inequality. We can thus relax the problem into
\begin{align}
   \label{eq:mindLP}
   \text{minimize } & \sum_{(u,v)\in E^-} w_{uv}(1-x_{uv}) + \sum_{(u,v)\in E^+} w_{uv}x_{uv} \\
   \text{subject to}& \quad x_{uw} \leq x_{uv} + x_{vw} \nonumber\\
   \phantom{subject to}& \quad 0 \leq x_{uv} \leq 1  \nonumber \\
   \phantom{subject to}& \quad x_{uv} = x_{vu}  \nonumber
\end{align}

\Textcite{ExactMIP13} solve this binary integer program on random instances and show that
depending on the negative edge density, the FICO Xpress solver starts to be unable to finish within
a one-hour time limit when $n \geq 40$.
\Textcite{Aref2016} describe four linear and quadratic  binary integer problems
to model \pcc{} with two clusters along with some preprocessing optimizations. With the Gurobi
software, they solve instances with up to $3200$ edges in less than a second. They also sketch
extensions to weighted graphs and more than two clusters.
In a different direction, \textcite{Berg2015}, encode the linear and quadratic integer formulations
into weighted MaxSAT instances and use the state of the art solver
MaxHS\footnote{\href{http://www.maxhs.org/}{http://maxhs.org}}~\autocite{SATSolver13} to get the
exact solution on instances with at most $1000$ nodes in less than a few hours.

exact describe the LP here
fpa

basically the problem is tractable when the number of disagreements is small, agreeing with our
bias. Likewise, exact methods works well when small rank, smart polytope in LP

\subsubsection{Hardness and approximations}
\label{ssub:cc_harness_approx}

Although the same problem was studied earlier~\autocites{Early96}{Ben-Dor99}, \textcite{Bansal2002}
coined the term \pcc{} and were the first to study this problem complexity. Namely, for complete,
unweighted signed graphs, they show that both \mind{} and \maxa{} are \NPc{}. Along the way, they
give a $17429$-approximation of \mind{} and a PTAS%
\bottomfootnote{An algorithm $\mathcal{A}$ is a \emph{polynomial-time approximation scheme (PTAS)} for a
minimization (respectively maximization) problem $\mathcal{P}$  in NP if given any $\epsilon>0$ and
any instance $x$ of $\mathcal{P}$ of size $n$, $\mathcal{A}$ produces, in time polynomial in $n$, a
solution that is within a factor $1+\epsilon$ (respectively $1-\epsilon$) of being optimal with
respect to $x$. Note that the time is not necessarily polynomial in $\epsilon$, so that a running
time of $O(n^{\frac{1}{\epsilon}})$ would qualify~\autocite[Definition 3.10]{CpxBook99}.}
that, for any $\epsilon \in [0,1]$, runs in
$O(n^2e^{O(\frac{1}{\epsilon^{10}}\log\frac{1}{\epsilon})})$ and returns with probability
$1-\frac{\epsilon}{3}$ a solution with at most $\epsilon n^2$ fewer agreements than the optimal
solution of \maxa{}.

\begin{table}[bt]
   \centering
   \small
   \caption{Hardness results of \pcc{}} \label{tab:cc_cpx}
   \begin{tabulary}{187mm}{lCCCC}
      \toprule
               & \multicolumn{2}{c}{\mind{}}   & \multicolumn{2}{c}{\maxa{}}                                   \\
      \cmidrule(r){2-3}
      \cmidrule(r){4-5}
      graph    & weighted                      & unweighted                                                     & weighted                                                     & unweighted                   \\
      \midrule
      Complete & \APXh{}~\autocite{Charikar2003} & \NPc{}~\autocite{Bansal2002}, \APXh{}~\autocite{Charikar2003}  &                                                              & \NPc{}~\autocite{Bansal2002} \\
      General  & \APXh{}~\autocites{Charikar2003}{Demaine2003} &  \APXh{}~\autocites{Charikar2003}{Emanuel2003}   & \multicolumn{2}{c}{\APXh{}~\autocite[Thm. 9]{Charikar2003}} \\
      \bottomrule
   \end{tabulary}
\end{table}

The next year, several authors independently strengthened these results and extended them to
weighted and general graphs, as summarized in \autoref{tab:cc_cpx}. In the most complete paper,
\textcite{Charikar2003} show that on complete graphs, minimizing disagreements is \APXh{},
\enquote{that is, is NP-hard to approximate within some constant factor greater than one} (it would
be nice to provide some intuition why it's more difficult to minimize disagreements but according to
the authors themselves, their reduction is \enquote{somewhat intricate}). They prove the same result
on general graphs, for \mind{} by using a reduction from the multicut problem \autocite[Theorem
8]{Charikar2003}\footnote{This reduction was actually turned into an equivalence, as we describe
in more details in \autoref{ssub:cc_under_stability_assumption}.}

We first give more details on the equivalence between \mmc{} and \pcc{},
following~\autocite{Demaine2006} but omitting the full proofs to avoid redundancy. Recall that given
a weighted graph $H=(V_H, E_H, w_H)$ and a collection of $k$ sources and targets
$S=\{(s_i,t_i)\}_{i=1}^k \in V_H^2$, in \mmc{} we want to find the lightest set of edges $T\in E_H$
whose removal disconnects every pair $s_i$ from the corresponding $t_i$. Let us first describe a
polynomial reduction from \mmc{} to \pcc{}. Namely, given an instance $(H, S)$ of \mmc{}, we let
$W_H=\sum_{e\in E_H} w_H(e)$ be the total weight of $H$ and $G_H$ be the same graph as $H$ with all
its edges labeled positively. We then connect every pair $(s_i, t_i)$ by a negative edge of weight
$W_H+1$. One can check (\autocite[Theorem 4.7]{Demaine2006}) that a multicut $T$ in $H$ with weight
$W$ induces a clustering in $G_H$ of weighted disagreement $W$ by the connected components of
$G^+\setminus T$. Likewise, a clustering of $G_H$ with weight $W$ induces a multicut on $H$ with
weight as most $W$. In the unweighted case, the reduction is similar but the heavy negative edges
are simulated in the following way: include every source and target in a clique of $n$ nodes and
connect that clique to the corresponding source or target by $n$ negative edges.

We next present the polynomial reduction from \pcc{} to \mmc{}. Given $G=(V, (E^+, E^-), w)$ we let
$H_G$ be the graph induced by $E^+$ with the same weight. Then for every negative edge $(u,v)$ of
weight $w_{uv}^-$, we create a new vertex $v_{\widehat{uv}}$, connect $u$ to $v_{\widehat{uv}}$ with
weight $w_{uv}^-$ and let $(v_{\widehat{uv}}, v)$ be a source-target pair added to $S_G$. This
construction is depicted in \autoref{fig:cc_mmc} and one can show (\autocite[Theorem
4.4]{Demaine2006})\Todo{give the intuition of the proof} that it takes a linear time to construct a
multicut of weight $W$ in $H_G$ from a clustering of weight $W$ in $G$, and vice versa.

\begin{figure}[htpb]
   \centering
   \includegraphics[width=0.8\linewidth]{assets/raw/cc_to_mmc.png}
   \caption{The transformation from \pcc{} on $G$ to \mmc{} on $H$ (temporarily reproduced from
   \autocite{Demaine2006}) \label{fig:cc_mmc}}
\end{figure}

which asks for the minimum weight set of edges whose removal in $G$ disconnect the
$k$ pairs $(s_i, t_i)$ and for \maxa{} by a reduction from MAX 3SAT~\autocite[Theorem
9]{Charikar2003}. The multicut reduction yields a $O(\log n)$ approximation bound, which is achieved
by rounding the canonical Linear Program~\eqref{eq:mindLP}.
Once the LP \eqref{eq:mindLP} is solved, we interpret $x_{uv}$ as a distance: the larger it is and
the more we want $u$ and $v$ to be in different clusters. We can then use the \regionGrow{}
method~\autocite{RegionGrowing93}. Namely, we pick a ball center $u$ \uar{} with radius \shalf{}: if
the average distance of the nodes in the ball to $u$ is less than $\nicefrac{1}{4}$, the ball forms a
cluster, otherwise $\{u\}$ forms a singleton cluster. We then remove the corresponding nodes from
the graph and repeat until all nodes are clustered. As we shall see, this method has been re used
with variations on the LP or on the two thresholds \shalf{} and $\nicefrac{1}{4}$.

However, \textcite[Theorem 2]{Charikar2003} note that the LP formulation has a poor integrality gap
when it comes to \maxa{}, thus they turn to a Semi Definite Program. Say that each cluster is
associated with a basis vector, then for each node $u$ in a cluster, we set $a_u$ to be the
corresponding basis vector. If $u$ and $v$ are in the same cluster, we then have $a_u\cdot a_v = 1$
while if they belong to different clusters, $a_u\cdot a_v = 0$. The weighted number of agreements
can then be represented by
\begin{align}
   \label{eq:maxaSDP}
   \text{maximize } & \sum_{(u,v)\in E^+} w_{uv}(a_u\cdot a_v) + \sum_{(u,v)\in E^-} w_{uv}(1-a_u\cdot a_v) \\
   \text{subject to}& \quad a_u\cdot a_u=1 \nonumber\\
   \phantom{subject to}& \quad a_u\cdot a_v\geq 0  \nonumber
\end{align}
After solving the SDP, a clustering can be obtained by a general rounding technique $H_t$: pick $t$
random hyperplanes and divides the nodes in $2^t$ clusters. \Textcite[Theorem 3]{Charikar2003} prove
that taking the best results of $H_2$ and $H_3$ gives in a $0.7664$ approximation on general graph.
This was slightly improved to $0.7666$ by \textcite{Swamy2004} with a different rounding: pick $k$
random unit vectors (called \emph{spokes}) and assign each $a_u$ to the closest spoke.

Combining \mind{} and \maxa{}, \textcite[Section 4]{Charikar2004} give a $\Omega(\frac{1}{\log n})$
approximation of the \textsc{MaxCorr} problem, which is maximizing \eqref{eq:maxa} - \eqref{eq:mind}
and can be formulated as a quadratic programming problem solved in polynomial time.

In complete graphs, \textcite[Section 3]{Charikar2003} also give an improved $4$-approximation to
\mind{}, by rounding the same LP and using its solution in randomized algorithm. We will not
describe it in detail since a similar idea was used by \textcite{CCPivotConf05} with a better
approximation. To explain it, we first describe their randomized combinatorial algorithm \ccpivot{},
which gives a $3$-approximation of \mind{} on complete unweighted graphs (it has later been
derandomized while preserving its approximation guarantee~\autocite{derandomCCPivot08}). At each
iteration, we pick a node $u$ \uar{} (called the pivot) and we create a cluster containing $u$ and all its neighbors
linked by a positive edges. On weighted complete graphs, they tweak this algorithm by using the
solution of the  LP~\eqref{eq:mindLP} to obtain different approximation factor depending on the
constraints imposed on the weight.\Todo{Comment on those constraints, especially the triangular ones
in the context of consensus clustering.} Recall that in the general formulation of the problem, each
edge carries two positive numbers: $w_{u,v}^+$ and $w_{u,v}^-$. If the weights respect the
probability constraints stating that for all edge $(u,v)$ in $E$, $w_{u,v}^+ + w_{u,v}^- = 1$, this
tweaking provide a $2.5$-approximation. Note that unweighted graphs naturally fit into that case, as
each edge is either labeled $+$ or $-$. If the weights
additionally respect the triangular inequality constraints stating that $w_{u,v}^- \leq w_{u,w}^- +
w_{w,v}^-$, this become a $2$-approximation. After solving the LP~\eqref{eq:mindLP} with additional
probability constraints, when picking a node $u$, each of its neighbors $v$ is added to the cluster
of $u$ with probability $x_{uv}$. \Textcite{Chawla2014} improve these two factors to respectively
$2.06$ and $1.5$ by exploiting the same idea but setting the probability to include each neighbor
$v$ of $u$ in the cluster of $u$ to be $1-f^+(x_{uv})$ if $(u,v)\in E^+$ and $1-f^-(x_{uv})$ if
$(u,v)\in E^-$, with a careful choice of $f^+$ and $f^-$. They also give a derandomized version of
their algorithm in the full version of the paper~\autocite[Theorem 23]{ChawlaArxiv14}.

\begin{table}
   \begin{tabulary}{187mm}{llcLL}
      \toprule
                                &            & $k$   & \mind{}                                                                & \maxa{}                                                     \\
      \midrule
      \multirow{2}{*}{Complete} & unweighted &       & $2.06$ \autocite{Chawla2014}                                           & PTAS from \textcite{Bansal2002}  \\
      \cmidrule(r){4-4}
                                & weighted   &       & $1.5$ (with triangular inequality) \autocite{Chawla2014}               &  and by setting $k=\Omega(1/\epsilon)$ \autocite{Giotis2006}  \\
      \midrule
   \multirow{3}{*}{General}     & unweighted &       & \multicolumn{2}{c}{No specific results for the unweighted case}                                                                       \\
      \cmidrule(r){4-5}
                                & weighted   & $k=2$ & $O(\sqrt{\log n})$ \autocite{Giotis2006}                               & $0.884$ \autocite{Mitra2009}                                  \\
      \cmidrule(r){4-5}
                                & weighted   &       & $O(\log n)$ \autocite{Charikar2003}, optimal under the UCG conjecture  & $0.7666$ \autocite{Swamy2004}                                 \\
      \bottomrule
   \end{tabulary}
   \caption{Best results on various problem.\label{tab:cc_approx}}
\end{table}

This concludes the presentation of the known approximation results on \pcc{}, that we summarize in
\autoref{tab:cc_approx}.

@@

As mentioned earlier, not having to set the number of clusters is an
attractive feature of the \pcc{} problem, but in some cases we may want to use prior knowledge.  The
problem was studied by \textcite{Giotis2006} on general graphs and we compile their results in
\autoref{tab:cc_fixed}. On complete unweighted graphs and with $k$ being the number of clusters, they
provide PTASs for \maxa{}$[k]$ running in $nk^{O(\epsilon^{-3}\log(\frac{k}{\epsilon}))}$ time and for
\mind{}$[k]$ running in $n^{O\left(\epsilon^{-2} 9^k\right)}\log(n)$ time. The latter was improved by
\textcite{LinearMinPTAS09}, with a PTAS running in $n^2 2^{O\left(\epsilon^{-3}k^6\log d\right)}$
and that can handle weighted graphs. For $k=2$, \mind$[2]$ admits a faster local search method with a
factor $2$ approximation~\autocite{Coleman2008}.
For complete weighted graph, \textcite{WeightedMaxAPTAS08} provide a PTAS for
\maxa{}$[k]$ under the condition that the ratio between the largest and smallest weights is bounded by a
constant.

\begin{table}[htpb]
   \centering
   \caption{Approximation results for \pcc{} on general graph with $k$ clusters} \label{tab:cc_fixed}
   \begin{tabulary}{187mm}{lLL}
      \toprule
      $k$	 & 2 & $\geq 3$ \\
      \midrule
      \maxa{} & 0.878 (improved to 0.884 by \autocite{Mitra2009}) & 0.7666 \autocite{Swamy2004} \\
      \mind{} & $O(\sqrt{\log n})$ as it reduces to Min 2CNF Deletion for which \textcite{min2CNF05}
      give such an approximation &
      this can be reduced from $k$-coloring, which for any $\epsilon > 0$ is \NPc{} to approximate
      within $n^{1-\epsilon}$ \autocite{InnaproxChroma07} \\
      \bottomrule
   \end{tabulary}
\end{table}

summary APX hard by equivalence with multicut (what about complete)? 3 strategies for approximation
(in rewrote) -> needs for heuristics
To summarize, there are currently three main approaches to approximate \mind{}. On a general graph,
one first solve the canonical linear program, and use the \regionGrow{} method to round the
fractional solution, resulting in an O(log n) approximation. On complete graphs, the simplest
solution is the \ccpivot{} algorithm, that grows clusters out of randomly selected pivots, in a way
reminiscent of the proof of thm. The approximation factor of this general idea can be improved by
interpreting the fractional solution of the linear program as probability to be included in the
pivot's cluster

\subsubsection{Heuristics}
\label{ssub:cc_heuristics}

\paragraph{Greedy methods}
\label{par:cc_greedy}

@@

% something about local minima when defining another energy function, and how it is achieved by a
% dynamic model but to be honest it has little to do with clustering {Marvel2009landscape}
% does it have something to do with phase transition
% Kappes2016 \enquote{Furthermore, due to the lack of an external field (unary terms), any permutation of an
% optimal assignment results in another optimal labeling.}
% like an ICML'17 paper that touches something very related (multicut) and gives recent applications in
% vision https://arxiv.org/abs/1503.03791 represents a cut by the set of interclusters edges

\subsubsection{Active and online settings}

Except for the local algorithms of \textcite{Bonchi2013}, all works presented so far considered the
batch case of \pcc{}, where the whole graph and all the signs are available at all time and with no
cost. This might not always be the case, for instance if the graph is too large to fit in memory or
if the edge labels are given by an expensive external procedure.

% \emph{Still have to write this part. Is there a link between mistake bound and approximation
% ratio?} say I have a binary classifier that perfectly predict sign wrt to the optimal clustering
% C* those below are more concerned with sign prediction than clustering per se Beside batch
% setting, one can also consider active \autocites{Cesa-Bianchi2012b}{Cesa-Bianchi2012a} and online
% \autocite{Gentile2013} framework.
% \enquote{the work of Cesa-Bianchi et al. [CBGV+12] that take a learning-theoretic perspective on the
% problem of predicting signs. They consider three types of models: batch, online, and active
% learning, and provide theoretical bounds for prediction mistakes for each setting. They use the
% correlation clustering objective as their learning bias, and they show that the risk of the
% empirical risk minimizer is controlled by the correlation clustering objective.}

Case in point, in the context of entity resolution, \textcite{activeCoref07} consider the \pcc{}
problem where, by querying an oracle, one can either reduce the uncertainty about one edge weight or
add an extra node with edges connecting it to existing nodes. However, this requires web queries
that are resource bounded and thus yields an active setting learning problem, where one has to
choose the most informative
queries given a budget. A formal definition is given in~\autocite{queryMoreEdgeCC07} and in
practice, after finding an initially good partition, they select in each cluster a node to be its
centroid, and query the edges connecting the centroid as ordered by an entropy-based criterion.
In the case the oracle answering the queries is consistent, then there exists an information
theoretic bound on the number of queries needed to recover the clusters, and an algorithm matching
that bound up to a $O(\log n)$ factor~\autocite{perfectActiveLong17}.
\textcite[Section 5]{Ailon2014} present another active algorithm that solves \mind$[k]$ with a
linear number of queries but an exponential running time in $n$.  In a noisy setting,
\textcite{Mitzenmacher2016} assume there is a planted $k$-partition and that we have access to an
oracle that for $u,v\in V^2$ returns $\cluster(u) - \cluster(v) \mod k$ with probability $1-p$ and a
noisy $\cluster(u) - \cluster(v) \pm 1 \mod k$ otherwise. For $k=2$, this is exactly $2$-\pcc{},
whereas for $k>2$, the oracle gives more information than simply the sign of the path from $u$ to
$v$. Whenever
$p < \shalf$, they show that $O(n^{1+\frac{1}{\log\log n}}\log n)$ queries are enough are to recover
the planted partition in polynomial time and with high probability. Those queries are actually
random (\ie{} non-adaptive), and the clusters are found by looking at almost edge-disjoint path
between all pairs of nodes.

In the online setting, \textcite{greedyOnline10} give a greedy algorithm that upon node arrival creates a
singleton cluster and then merge all pairs of clusters for which it increases the total number of
agreements. For \mind{}, this is $O(n)$-competitive algorithm and they show such ratio is optimal by
exhibiting an instance\footnote{Namely, two positive cliques $A$ and $B$ joined by positive edges except
between $a\in A$ and $\{b_1,\ldots, b_k\}\in B$. Those nodes are given first and thus form a cluster,
which yields at least one disagreement every time one the $n-(k+1)$ remaining nodes is added.} on
which any strategy ends up with $n - k$ disagreements whereas optimal cost is $k$. On the \maxa{}
side, this greedy strategy result in a $\shalf$-competitive algorithm. If it is randomly mixed with a
\textsc{Dense} variation, it increases to $\shalf+\eta$, still far from the demonstrated $0.834$ upper
bound.
% when the graph is given node by node,
% \url{https://link.springer.com/chapter/10.1007/978-3-319-18173-8_7} show to cluster it in static
% clique, so it sounds related to cluster editing, except their objective is to maximize the
% fraction of edge in cliques (ie avoid small cluster)

\bigskip

full conc of the section: the problem is difficult. However, it can be solved with guarentees in
theory (because LP are not practical) and in efficiently in practice (using pivot as initilizatin
for instance). Furthermore, instances obeying our bias can be solved much better. We next present
settings where we are close to that bias
